### 2023-11-20 main.tex
''

	\Omega^{'}=\bigotimes_{x=1}^{L}\Omega_{x}^{'}\qquad \Omega_{x}^{'}=\left\{|\tau_{x}\rangle\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}

@@

% However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 
 \begin{flushright}
     $\square$
 \end{flushright}
 \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need to transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $u(x)$. % that we connect to every site $x\in V$ of the graph $G$. \\
 Considering $A,B\in gl(N)$, the Hadamard formula reads 
 \begin{equation}\label{HadamardFormula}
     \exp{(-B)}A\exp{(B)}=A-\left[B,A\right]+\frac{1}{2!}\left[B,\left[B,A\right]\right]-\frac{1}{3!}\left[B,\left[B,\left[B,A\right]\right]\right]+\ldots
 \end{equation}
In the following we need the application of this with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra $gl(N)$ with $c,d\in\{1,\ldots,N\}$. Therefore we compute 
\begin{align}
	\left[B,A\right]=\sum_{a=1}^{N-1}\left[E_{aN},E_{cd}\right]=\delta_{cN}\sum_{a=1}^{N-1}E_{ad}-(1-\delta_{dN})E_{cN}
\end{align}
and 
\begin{align}
	\left[B\left[B,A\right]\right]=&\left[\sum_{a=1}^{N-1}E_{aN},\delta_{cN}\sum_{b=1}^{N-1}E_{bd}-(1-\delta_{dN})E_{cN}\right]\nonumber\\=&
	\sum_{a=1}^{N-1}\left(\delta_{cN}\sum_{b=1}^{N-1}\left[E_{aN},E_{bd}\right]-(1-\delta_{dN})\left[E_{aN},E_{cN}\right]\right)\nonumber\\=&
	\sum_{a=1}^{N-1}\left(-\delta_{cN}\delta_{ad}\sum_{b=1}^{N-1}E_{bN}-(1-\delta_{dN})\delta_{cN}E_{aN}\right)\nonumber\\=&
	-\left(\delta_{cN}(1-\delta_{dN})+(1-\delta_{dN})\delta_{cN}\right)\sum_{b=1}^{N-1}E_{bN}\nonumber
	\\=&
	-2\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}
\end{align}
From the third commutator on we always obtain zero, i.e. $[B,[B,[B,A]]]=0$. All in all we have that 
 \begin{align}\label{HT-BA}
 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\delta_{cN}\sum_{a=1}^{N-1}E_{ad}+(1-\delta_{dN})E_{cN}-\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}\dt
 \end{align}
\begin{comment}
\begin{enumerate}
    \item for $A=E_{b N}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT_El1}
        \exp{(-E)}E_{b N}\exp{(E)}=E_{b N}
    \end{equation}
    because $E_{b N}$ commutes with $E$
    \item for $A=E_{bb}$ with $b \in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT_Ell}
        \exp{(-E)}E_{b b}\exp{(E)}=E_{b b}+E_{b N}
    \end{equation}
Indeed, using \eqref{eq:comgl} we have 
    \begin{equation}
       \left[E, E_{bb}\right]=\sum_{a=1}^{N-1}\left(E_{ab}\delta_{b N}-E_{b N}\delta_{ab}\right)=-E_{bN}
    \end{equation}
    Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
    \item for $A=E_{Nb}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT-E1l}
        \exp{(-E)}E_{N a}\exp{(E)}=E_{Na}+E_{NN}-\sum_{c=1}^{N-1}\left(E_{cN}+E_{ca}\right)
    \end{equation}
  %\com{Why indices have names $b, k, j, a, b$? Fix one set for the generators}

@@

%In this notation, the elements of the duality matrix reads
%\begin{equation}\label{ElementsDualityMatrixChain_1}
%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
%\\
Using duality, one can compute the  $m$-point correlations between non-empty particles in terms of the absorption probabilities of $m$ dual particles. Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities.  %For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. 
\begin{corollary}[Correlations via duality]
\label{prop-absorbing}
Consider $m\in \{1,\ldots,L\}$ and let $a_{k}\in\{1,\ldots,N-1\}$ species positioned at sites $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$. Then, the $m$-point correlations in the non-equilibrium steady state (NESS) read
\begin{equation}
\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
is the  probability that  $t_{k}$ dual particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$. The dual initial configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
\label{xsi-init}
	\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
	\end{cases}
\end{equation}
\end{corollary}
\textbf{Proof}:
For any $\bm{\tau}\in \Omega^{'}$ the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} evaluated on the dual configuration $\bm{\xi}\in\widetilde{\Omega}$ given in \eqref{xsi-init} read
\begin{equation}
	D(\bm{\tau},\bm{\xi})%=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}
	=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
\end{equation}
Therefore, by duality and ergodicity we have 
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})\dt
\end{split}
\end{equation}
\begin{flushright}
	$\square$
\end{flushright} 
    \begin{corollary}
ADD
\end{corollary}

@@

and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu_{\text{NESS}}$ are given by 

@@

\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})

@@

	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}

@@

%				\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(L+1)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)

@@

We consider the average with respect to $\mu_{\text{NESS}}$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads

@@

%\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt

@@

	 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{(L+1)}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\dt

@@

We consider the average with respect to $\mu_{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$. 

@@

%		 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt

@@

Then, by using \eqref{exactCorrelations} we have 
	\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]=&\frac{x_{1}(x_{2}-1)}{L(L+1)}\beta_{a_{1}}\beta_{a_{2}}+\frac{x_{1}(L+1-x_{2})}{L(L+1)}\beta_{a_{1}}\alpha_{a_{2}}\\
	+&\frac{x_{2}(L+1-x_{1})}{L(L+1)}\alpha_{a_{1}}\beta_{a_{2}}+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}\alpha_{a_{1}}\alpha_{a_{2}}

@@

%	 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt

@@

		 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt

@@

We consider the average with respect to $\mu_{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$. Using \eqref{abs-probabilities} we compute the absorption probabilities 

@@

Then, by using \eqref{exactCorrelations} we obtain 
\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\frac{x_{1}(x_{2}-1)(x_{3}-2)}{L(L^{2}-1)}&\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
	(x_3-2)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\
+\frac{x_1 (L (-x_3)+L+x_2 (x_3-2)+1)}{L(L^2-1)}&\beta_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{x_1 (x_2-1) (L-x_3+1)}{L \left(L^2-1\right)}&\beta_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
+ \frac{(L-1) x_2 (x_3-1)-x_1 (x_2-1)
	(x_3-2)}{L \left(L^2-1\right)}& \alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_3+1) (x_2 (L-x_1-1)+x_1)}{L
	\left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
+\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L^{2}-1)}&\alpha_{a_{1}}\alpha_{a_{2}}\alpha_{a_{3}}

@@

\begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Section 4.3 of \cite{vanicat2017exact}.

@@

	|V \rangle\nonumber&=

>>>>

	\Omega^{'}=\left\{(\tau_{1},\ldots,\tau_{L})\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}

@@

% However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 
 \begin{flushright}
     $\square$
 \end{flushright}
 \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $u(x)$. % that we connect to every site $x\in V$ of the graph $G$. \\
 Considering $A,B\in gl(N)$, the Hadamard formula reads 
 \begin{equation}\label{HadamardFormula}
     \exp{(-B)}A\exp{(B)}=A-\left[B,A\right]+\frac{1}{2!}\left[B,\left[B,A\right]\right]-\frac{1}{3!}\left[B,\left[B,\left[B,A\right]\right]\right]+\ldots
 \end{equation}
In the following we need the application of this with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra $gl(N)$ with $c,d\in\{1,\ldots,N\}$. Therefore we compute 
\begin{align}
	\left[B,A\right]=\sum_{a=1}^{N-1}\left[E_{aN},E_{cd}\right]=\delta_{cN}\sum_{a=1}^{N-1}E_{ad}-(1-\delta_{dN})E_{cN}
\end{align}
and 
\begin{align}
	\left[B\left[B,A\right]\right]=&\left[\sum_{a=1}^{N-1}E_{aN},\delta_{cN}\sum_{b=1}^{N-1}E_{bd}-(1-\delta_{dN})E_{cN}\right]\nonumber\\=&
	\sum_{a=1}^{N-1}\left(\delta_{cN}\sum_{b=1}^{N-1}\left[E_{aN},E_{bd}\right]-(1-\delta_{dN})\left[E_{aN},E_{cN}\right]\right)\nonumber\\=&
	\sum_{a=1}^{N-1}\left(-\delta_{cN}\delta_{ad}\sum_{b=1}^{N-1}E_{bN}-(1-\delta_{dN})\delta_{cN}E_{aN}\right)\nonumber\\=&
	-\left(\delta_{cN}(1-\delta_{dN})+(1-\delta_{dN})\delta_{cN}\right)\sum_{b=1}^{N-1}E_{bN}\nonumber
	\\=&
	-2\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}
\end{align}
From the third commutator on we always obtain zero, i.e. $[B,[B,[B,A]]]=0$. All in all we have that 
 \begin{align}\label{HT-BA}
 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\delta_{cN}\sum_{a=1}^{N-1}E_{ad}+(1-\delta_{dN})E_{cN}-\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}\dt
 \end{align}
\begin{comment}
\begin{enumerate}
    \item for $A=E_{b N}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT_El1}
        \exp{(-E)}E_{b N}\exp{(E)}=E_{b N}
    \end{equation}
    because $E_{b N}$ commutes with $E$
    \item for $A=E_{bb}$ with $b \in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT_Ell}
        \exp{(-E)}E_{b b}\exp{(E)}=E_{b b}+E_{b N}
    \end{equation}
Indeed, using \eqref{eq:comgl} we have 
    \begin{equation}
       \left[E, E_{bb}\right]=\sum_{a=1}^{N-1}\left(E_{ab}\delta_{b N}-E_{b N}\delta_{ab}\right)=-E_{bN}
    \end{equation}
    Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
    \item for $A=E_{Nb}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT-E1l}
        \exp{(-E)}E_{N a}\exp{(E)}=E_{Na}+E_{NN}-\sum_{c=1}^{N-1}\left(E_{cN}+E_{ca}\right)
    \end{equation}
  %\com{Why indices have names $b, k, j, a, b$? Fix one set for the generators}

@@

%In this notation, the elements of the duality matrix reads
%\begin{equation}\label{ElementsDualityMatrixChain_1}
%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
%\\
Using duality, one can compute the  $m$-point correlations between non-empty particles in terms of the absorption probabilities of $m$ dual particles. Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities. In the following we denote by $\mu$ the non-equilibrium steady state distribution. %For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. 
\begin{corollary}[Correlations via duality]
\label{prop-absorbing}
Consider $m\in \{1,\ldots,L\}$ and let $a_{k}\in\{1,\ldots,N-1\}$ species positioned at sites $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$. Then, the $m$-point correlations in the non-equilibrium steady state (NESS) read
\begin{equation}
\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
is the  probability that  $t_{k}$ dual particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$. The dual initial configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
\label{xsi-init}
	\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
	\end{cases}
\end{equation}
\end{corollary}
\textbf{Proof}:
For any $\bm{\tau}\in \Omega^{'}$ the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} evaluated on the dual configuration $\bm{\xi}\in\widetilde{\Omega}$ given in \eqref{xsi-init} read
\begin{equation}
	D(\bm{\tau},\bm{\xi})%=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}
	=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
\end{equation}
Therefore, by duality and ergodicity we have 
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})\dt
\end{split}
\end{equation}
\begin{flushright}
	$\square$
\end{flushright} 
\begin{remark}
	The result written in the previous Corollary \ref{prop-absorbing} holds also for chains with higher maximal occupancy ($\nu>1)$, as specified in Section \ref{Subsection-ss-nonI}. 
\end{remark}
    \begin{corollary}
ADD
\end{corollary}

@@

and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu$ are given by 

@@

\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})

@@

	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}

@@

%				\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(L+1)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)

@@

We consider the average with respect to $\mu$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads

@@

%\mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt

@@

		\langle\rho_{a_{1}}^{x_{1}}\rangle= \mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{(L+1)}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\dt

@@

We consider the average with respect to $\mu$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$. 

@@

%		 \mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt

@@

%Then, by using \eqref{exactCorrelations} we have 
%\begin{split}
%	\mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]=&\frac{x_{1}(x_{2}-1)}{L(L+1)}\beta_{a_{1}}\beta_{a_{2}}+\frac{x_{1}(L+1-x_{2})}{L(L+1)}\beta_{a_{1}}\alpha_{a_{2}}\\
%	+&\frac{x_{2}(L+1-x_{1})}{L(L+1)}\alpha_{a_{1}}\beta_{a_{2}}+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}\alpha_{a_{1}}\alpha_{a_{2}}
%\end{split}

@@

%	 \mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt

@@

		 \mathbb{E}_{\mu}\left[\left(\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt

@@

We consider the average with respect to $\mu$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$. Using \eqref{abs-probabilities} we compute the absorption probabilities 

@@

%Then, by using \eqref{exactCorrelations} we obtain 
%\mathbb{E}_{\mu}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\frac{x_{1}(x_{2}-1)(x_{3}-2)}{L(L^{2}-1)}&\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
%	(x_3-2)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\
%+\frac{x_1 (L (-x_3)+L+x_2 (x_3-2)+1)}{L(L^2-1)}&\beta_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{x_1 (x_2-1) (L-x_3+1)}{L \left(L^2-1\right)}&\beta_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
%+ \frac{(L-1) x_2 (x_3-1)-x_1 (x_2-1)
%	(x_3-2)}{L \left(L^2-1\right)}& \alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_3+1) (x_2 (L-x_1-1)+x_1)}{L
%	\left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
%+\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L^{2}-1)}&\alpha_{a_{1}}\alpha_{a_{2}}\alpha_{a_{3}}

@@

\begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with those found in Section 4.3 of \cite{vanicat2017exact}.

@@

	|V \rangle=
